---

---
title: "Palm Trees"
description: "An exploration of palm tree data"
author: "Tyler Rhee"
format: html
execute:
  warning: false
  message: false
---

# Introduction

This project that I'm doing explores a dataset about palm trees which I will exmaine the data and then create a visualization to interpret the patterns in different palm tree data.


## Load the data

```{r}
palmtrees <- readr::read_csv(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-03-18/palmtrees.csv"
)

```
---


## Check the data

```{r}
names(palmtrees)
```


## Visualize the data

This graph shows the 10 most common palm tree genera in the dataset.



```{r}
top_genera <- palmtrees |>
  dplyr::filter(!is.na(acc_genus)) |>
  dplyr::count(acc_genus, sort = TRUE) |>
  dplyr::slice_head(n = 10)

ggplot2::ggplot(
  top_genera,
  ggplot2::aes(x = reorder(acc_genus, n), y = n)
) +
  ggplot2::geom_col() +
  ggplot2::coord_flip() +
  ggplot2::labs(
    title = "10 Most Common Palm Tree Genera",
    x = "Genus",
    y = "Number of Records"
  )
```

## Sources

- [TidyTuesday Palm Trees dataset and README](https://github.com/rfordatascience/tidytuesday/tree/main/data/2025/2025-03-18)
- [TidyTuesday project](https://github.com/rfordatascience/tidytuesday)